Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-07-06 write-ups/FSE/paper.tex
added updated licensing

%%% The following is specific to ESEC/FSE'17 and the paper
%%% 'Cooperative Kernels: GPU Multitasking for Blocking Algorithms'
%%% by Tyler Sorensen, Hugues Evrard, and Alastair F. Donaldson.
%%%
%%% If you see 'none' in the 'setcopyright' statement below,
%%% please first submit your publishing-rights agreement with ACM (follow link on submission page),
%%% and then visit the instructions page again (follow link in author-kit message)
%%% in order to copy the correct 'setcopyright' statement.  Please contact us in case of questions.
%%%
\setcopyright{none}
\acmDOI{10.1145/3106237.3106265}
\acmISBN{978-1-4503-5105-8/17/09}
\acmConference[ESEC/FSE'17]{2017 11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{September 4-8, 2017}{Paderborn, Germany} 
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

>>>>

%%% The following is specific to ESEC/FSE'17 and the paper
%%% 'Cooperative Kernels: GPU Multitasking for Blocking Algorithms'
%%% by Tyler Sorensen, Hugues Evrard, and Alastair F. Donaldson.
%%%
\setcopyright{acmlicensed}
\acmDOI{10.1145/3106237.3106265}
\acmISBN{978-1-4503-5105-8/17/09}
\acmConference[ESEC/FSE'17]{2017 11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{September 4--8, 2017}{Paderborn, Germany} 
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}
